Discovery of $r$-process stars in LAMOST

### 2018-01-25 article/ms.tex
new drapht, fixed some stuff

	\subsection{The rate of neutron star mergers, what we expect, what we find}
	From the recent aLIGO data \cite{LIGO2016}, we are able to find an estimate for an upper-bound frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}. 
	Using this we were able to find:
	\begin{itemize}
		\item An estimate for the amount of r-process stars that should be present in the Milky Way that have been enhanced through neutron star mergers. Assuming instant recycling in that any star that dies is instantly formed into a new star, also assuming that no r-process matter pollutes other stars by any other means than this. 
		\item An estimate of how many r-process enhanced giants should be present from an estimate number of the Milky Way's total stars.
		\item An estimate of how many r-process enhanced stars (giants or otherwise) that should be present from an estimate number of the Milky Way's total stars.
	\end{itemize}

@@

	In these calculations we also say that a star is said to be enhanced if [Eu/Fe] >= 0.7, and performed the low-bound estimate that all of our 47 stars exhibited this abundance. Additionally the amount of r-process material is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5}$.

@@

    We also find that, of our sample of $\approx450000$ giants, the amount of r-process enhanced stars we should have find comes to less than one (0.226). Similarly if we are to extend our sample from the 450000 giants supplied by Anna Ho, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should have found 1.11 stars enhanced in the r-process. While again this should be considered a lower bound, it is still a startling difference from the 47 that we found in our sample.

@@

	We recommend follow-up high resolution spectra be obtained for each of the 60 stars to ascertain how enhanced they are. To find the origin of these stars and to show whether or not they may come from a similar progenitor site it is necessary to find orbits for them. We encourage orbit analysis after further Gaia data releases should these stars be present in them.

>>>>

	\subsection{The rate of neutron star mergers, what we expect, what we find}
	From the recent aLIGO data \cite{LIGO2016}, we are able to find an estimate for an upper-bound frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}. 
	Using this we are able to find:
	\begin{itemize}
		\item An estimate for the amount of r-process stars that should be present in the Milky Way that have been enhanced through neutron star mergers. Assuming instant recycling in that any star that dies is instantly formed into a new star, also assuming that no r-process matter pollutes other stars by any other means than this. 
		\item An estimate of how many r-process enhanced giants should be present from an estimate number of the Milky Way's total stars.
		\item An estimate of how many r-process enhanced stars (giants or otherwise) that should be present from an estimate number of the Milky Way's total stars.
	\end{itemize}

@@

	In these calculations we also say that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the low-bound estimate that all of our 47 stars exhibited this abundance. Additionally the amount of r-process material expelled is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5}$.

@@

    We also find that, of our sample of $\approx450000$ giants, the amount of r-process enhanced stars we should find comes to less than one (0.224). Similarly if we are to extend our sample from the 450000 giants supplied by Anna Ho, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should have found 1.09 stars enhanced in the r-process. While again this should be considered a lower bound, it is still a startling difference from the 47 that we found in our sample.

@@

	We recommend follow-up high resolution spectra be obtained for each of the 47 stars to ascertain how enhanced they are. To find the origin of these stars and to show whether or not they may come from a similar progenitor site it is necessary to find orbits for them. We encourage orbit analysis after further Gaia data releases should these stars be present in them.
